Stage-Splitting a Modal Language

### 2014-07-30 paper/splitting.tex
added two more notes

We give the following end-to-end correctness lemmas for closed terms (open term versions forthcoming).

@@

>>>>

We give the following end-to-end correctness lemmas for closed terms. 
Open term versions forthcoming.
The jury is still out on how to make these strong enough to prove that the partitioning between stages is correct.

@@

You should think of these theorems as saying that 
splitting commutes with evaluation.
